Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-08-20 research_class/paper.tex
paper.tex: abstract, tasks, improved graphs.
- add missed kill_count command line.

\begin{abstract}
TODO: write an abstract.
\end{abstract}

@@

During the planning phase, the project was broken down into six
incremental steps:

@@

@@

Steps 1-5 were successfully implemented for this paper. Step 6 was an
aspirational goal because this functionality is not yet supported in
PeerJS although it is being tracked by issue report:
https://github.com/peers/peerjs/issues/103

@@

TBD: Setup for the automated tests.

Description of SlimerJS

Creation of SlimerJS test scripts using JavaScript.

@@

TBD: Outcome of the automated tests.

\begin{tikzpicture}
    \begin{axis}[
            title=Initial Cluster Activation,
            xlabel={Nodes},
            ylabel={Time (ms)},
            grid=major,
        ]
        \addplot table {data/data_cluster_up.dat};
    \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
    \begin{axis}[
            title=Message Propagation,
            xlabel={Nodes},
            ylabel={Time (ms)},
            grid=major,
        ]
        \addplot table {data/data_cluster_up.dat};
    \end{axis}
\end{tikzpicture}

\begin{tikzpicture}
    \begin{axis}[
            title=Node Failure Recovery,
            xlabel={Nodes},
            ylabel={Time (ms)},
            grid=major,
            legend entries={$Leader Down$,$Half Cluster Down$},
        ]
        \addplot table {data/data_kill_leader.dat};
        \addplot table {data/data_kill_half.dat};
    \end{axis}
\end{tikzpicture}

>>>>

\begin{abstract}
We describe the creation of a browser-based distributed peer-to-peer
chat application using WebRTC, PeerJS and Raft.js. WebRTC is
a protocol that modern browsers have begun to integrate which enables
browser-to-browser communication. PeerJS is a WebRTC client library
and extensible signalling server. Raft.js is an implementation in
JavaScript of the Raft distributed consensus protocol. These
technologies are combined to create a chat application that guarantees
a shared, consistent and linearized view of the chat history without
relying on a single centralized server. We also create a series of
automated tests using the SlimerJS browser automation tool and use
them to show the correctness of the chat application and also to
measure the performance and scalability of the application over
various cluster sizes.
\end{abstract}

@@

During the planning phase, the project was broken down into ten incremental steps:

@@

\item Sessionless/Datagram RPC messages: extend Raft RPC requests and response messages so that RPC responses have enough context to be handled separately from RPC requests. Specifically this enables Raft to support a datagram (sessionless) network transport.

\item Atomic state machine operations: implement a state machine update operation that succeeds against the specified key only if no other operation has been applied to a key since the last time the client read from that key.

\item Automatic client request forwarding: extend the client request RPC to also be sessionless/datagram based. Implement a asynchronous JavaScript function that determines which node is the leader and forwards client request RPCs to the leader. This function must also correlate responses to the client request and invoke the callback for the original request.

\item Chat application: add the ability to send a message to the chat log using the client request forwarding functionality with an atomic state machine operation. Show the current chat history based on the chat entries in the state machine.

@@

Steps 1-9 were successfully implemented for this paper. Step 10 was an
aspirational goal because this functionality is not yet supported in
PeerJS although it is being tracked by issue report:
https://github.com/peers/peerjs/issues/103

@@

TODO: Setup for the automated tests. Description of SlimerJS. Creation of SlimerJS test scripts using JavaScript.

@@

TODO: Outcome of the automated tests.

The following figure shows the amount of time that the cluster takes to
elect a leader and then reconfigure the cluster to the the final size
(adding one node a time).

\begin{tikzpicture}
    \begin{axis}[
            title=Initial Cluster Activation,
            xlabel={Nodes},
            ylabel={Time (seconds)},
            grid=major,
        ]
        \addplot table {data/data_cluster_up.dat};
    \end{axis}
\end{tikzpicture}

The following figure shows the amount of time that a stable cluster takes to
propagate, commit and apply a single state machine change to the state
machines on every cluster node.

\begin{tikzpicture}
    \begin{axis}[
            title=Message Propagation,
            xlabel={Nodes},
            ylabel={Time (ms)},
            grid=major,
        ]
        \addplot table {data/data_propagate.dat};
    \end{axis}
\end{tikzpicture}

The following figure shows the amount of time that it takes for
a stable cluster to recover (elect a new leader and remove the failed
servers from the cluster) when one or more nodes fails. The first line
shows the recovery time when just the leader fails. The second line
show the recovery time when one less than half of the nodes fail.

\begin{tikzpicture}
    \begin{axis}[
            title=Node Failure Recovery,
            xlabel={Nodes},
            ylabel={Time (seconds)},
            grid=major,
            legend entries={$Leader Down$,$Half Cluster Down$},
        ]
        \addplot table {data/data_kill_leader.dat};
        \addplot table {data/data_kill_half.dat};
    \end{axis}
\end{tikzpicture}
